---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, echo=FALSE, eval=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 1) Wokring with a package structure

For now I created a new project and copied the `DESCRIPTION` `NAMESPACE` and `/R` folder to the main package. 
```{r packagestructure}
#devtools::create("r.novice.inflammation")
```

# 2) The data

It is common to read your data within `data-raw/dataraw.R`. 
* use `devtools::use_data_raw()` to create the folder (I never make these folders manually in order to prevent spelling errors)
* Within `data-raw` I created the Rscript `dataraw.R`
* The script contains the following information:

```{r data}
library(data.table)
#car_data<-fread("_episodes_rmd/data/car-speeds.csv")
#devtools::use_data(car_data)
```

Within the folder `/data` a `.rda` file is create containing the information from the `.csv` file (you could also first make some modifications to the original dataset). 

# 3) The documentation

The documentation of data has similarities to the documentation of function within R. 

* Create a script named `data.R` within the `/R` folder
* The script contains documentation of your dataset which looks like:

```{r documentation}
#'Car Data
#'
#'This dataset contains information of the color, speed and state of cars.
#'
#'@format A data frame with 100 rows and 3 variables
#'\describe{
#' \item{Color}{The color of the car. These are characters}
#' \item{Speed}{The maximum speed of the car in m/s}
#' \item{State}{The state where the car was made}
#' }
"car_data"

```

* use `devtoools::document()` create the documentation, within the `/man` folder a `.Rd` file is created.

In order to see the documentation:

* `devtools::build()`
* `devtools::reload()`
* ?car_data

